---
title: "Introduction to dsamplr"
author: "Kieran Meteyard"
date: "March 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to dsamplr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r echo=FALSE}
library(dsamplr)
```


The dsamplr package provides a simple interface for sampling from a chosen statistical distribution. It allows the user to specify:

- The required number of samples
- The chosen distribtuion (currently limited to normal, poisson and binomial)
- Parameters for the chosen distribution

The package defines an S3 class object 'dsamplr' with a specified summary method. 

## Examples 
Sample 10 random draws from a normal distribution 

```{r}
dsamplr(10, "normal")
```

Sample 100 draws from a poisson distribution with lambda = 10 

```{r}
dsamplr(10, "poisson", lambda = 10)
```

The documentation for the underlying base R functions rnorm, rpois and rbinom provide more information on permitted inputs.

## dsamplr class

The output is returned as an S3 object of class 'dsamplr'. This is simply a list with samples stored at $sample and the distribution stored at $distribution. A summary method is also defined as shown below. 

```{r}
draw <- dsamplr(100, "normal")

draw$sample

draw$distribution

summary(draw)
```

## Pitfalls
Make sure to input the distribution as a string. Avoid the following:

```{r, error = TRUE}
dsamplr(100, normal)
```

